---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rscloud

<!-- badges: start -->
<!-- badges: end -->

API wrappers for the rstudio.cloud service.  The initial release includes APIs for managing space memberships, and listing projects within a space. 

## Getting started

To get started, you'll need to obtain credentials from the RStudio Cloud team and set the environment variables `RSCLOUD_CLIENT_ID` and `RSCLOUD_CLIENT_SECRET`. The recommended way to set these is by editing your `.Renviron` file. This can be easily done by calling the `usethis::edit_r_environ()` function. Your `.Renviron` file may look something like the following:

```
RSCLOUD_CLIENT_ID=xxxxxxx
RSCLOUD_CLIENT_SECRET=zzzzzzz
```

You can install the development version of rscloud as follows:

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("rstudio/rscloud")
```

The entry point to most of the functionality is a *space*. To see the list of spaces you have access to, you can use the `rscloud_space_list()` function:

```{r, include  = FALSE, eval = TRUE}
library(rscloud)
# clean up
space <- rscloud_space(31783)

members <- space %>% 
  space_member_list() %>% 
  dplyr::filter(email != "kevin.kuo+rscloud@rstudio.com")
space %>% 
  purrr::safely(space_member_remove)(members, ask = FALSE)

space %>% 
  purrr::possibly(space_invitation_list, otherwise =NULL)() %>% 
  purrr::safely(invitation_rescind)()
```


```{r}
library(rscloud)
rscloud_space_list()
```

To create a space object, use the `rscloud_space()` function:

```{r}
space <- rscloud_space(31783)
# you can also use the space name
# space <- rstudio_space(name = "test-space-1")
space
```

Adding members to a space can be done via `space_member_add()`:

```{r}
space %>% 
  space_member_add("kevin.kuo+test1@rstudio.com")

space
```

You can get a tidy data frame of space members with `space_member_list()`:

```{r}
space %>% 
  space_member_list()
```

You can also provide a data frame of user information, which can be useful when working with spreadsheets of class rosters:

```{r}
emails <- c("kevin.kuo+test2@rstudio.com", "kevin.kuo+test3@rstudio.com")
df <- tibble::tibble(user_email = emails)

space %>% 
  space_member_add(df)

space
```

You can also work with outstanding invitations:

```{r}
invitations <- space %>% 
  space_invitation_list()

invitations
```

To resend invitations, use the `invitation_send()` function:

```{r, eval = FALSE}
invitations %>% 
  # filter(...) %>% 
  invitation_send()
```
